A new method to estimate dark matter halo concentrations

### 2015-02-23 paper/article.tex
nueva grafica de velocity-density method

\subsection{Tests on N-body data}
\label{sec:data}
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{mass-velocity.pdf}
    \includegraphics[width=0.48\textwidth]{mass-density.pdf}
  \end{center}
  \caption{Comparison between the concentrations measured by our
    method and the maximum velocity (left) and density (right)
    methods. The line indicates the equal value between the two
    techniques.
  \label{fig:mdv}}
\end{figure*}

>>>>

\subsection{Tests on N-body data}
\label{sec:data}
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.33\textwidth]{mass-velocity.pdf}
    \includegraphics[width=0.33\textwidth]{mass-density.pdf}
    \includegraphics[width=0.33\textwidth]{density-velocity.pdf}
  \end{center}
  \caption{Comparison between the concentrations measured by our
    method and the maximum velocity (left) and density (middle)
    methods. The line indicates the equal value between the two
    techniques. The right panel compares the results of the maximum
    velocity and density methods.
  \label{fig:mdv}}
\end{figure*}
